Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-24 doc/PRF2022/PRF_main.tex
rheology refs added

The shear stress-strain rate data are excellently fit by power laws.
Figures~\ref{fig:rheologysummary}(a)--(c) show the data for Type I, Type
II and Type III JPs, respectively, under both shear flow (squares) and
TG flow (triangles). The bilayer phases consisting of Type I JPs are
basically Newtonian with viscosity $0.014$ MPa\;$\upmu$s $= 14$ mPa\;s,
about 14 times the viscosity of water at room temperature
(Figures~\ref{fig:rheologysummary}(a), dashed curve). The vesicle
bilayer phase is slightly shear thickening
(Figure~\ref{fig:rheologysummary}(a), solid curve). Similar shear
thickening behaviors are found in continuum vesicle
models~\cite{rah-vee-bir2010}. The multilamellar phase consisting of
Type II JPs is somewhat shear thinning, but its viscosity is larger than
for Type I. Finally, the striated phase is strongly shear-thinning. This
further explains the rigid-like behavior of the striated phase found in
the strain, shear-rate relationships from
Figures~\ref{fig:s2esummary}(a) and (b) (triangles).

@@

The calculated viscosities---14~mPa~s for Type I and 21~mPa~s for Type
II JP phases---are physically reasonable. In two-dimensional dilute
suspensions, the Einstein viscosity correction is $1 + 2 \phi + 4\phi^2
+ O(\phi^3)$, where $\phi \ll 1$ is the volume
fraction~\cite{PhysRevFluids.1.043301, Haines2011APO, Khair2006TheC,
Brady1983TheEV}. In Figures~\ref{fig:s2esummary}(e)--(h), the volume
fraction is $\phi \approx 0.5$, which would correspond to a effective
shear viscosity of $4$~mPa~s according to Einstein's viscosity
correction. Note, however, that since $\phi = 0.5$ is outside of the
dilute limit, one expects viscosities ten or more times greater than the
viscosity of water~\cite{Konijn2014ExperimentalSO}.

Nevertheless, further simulations are required to differentiate between
purely suspension effects and particles' preferred alignments. For
example, the difference between the values 14~mPa~s for Type I and
21~mPa~s for Type II JPs can be explained by the fact that the
multilamellar phase is more tightly packed than the bilayer phase
(Figures \ref{fig:s2esummary}(e)--(h)). Furthermore, it seems that the
viscosity, and the tendency toward shear thinning in the case of Type
III JPs where viscosity is effectively infinite for low strain rates
(Figure \ref{fig:rheologysummary}(c)), is related to particle
coordination. To leading order, a single particle coordinates with: one
neighbor in the apposing bilayer for Type I, two neighbors at the tail
and head interfaces for Type II, and four neighbors (front, back, left,
and right) for Type III.

>>>>

The shear stress-strain rate data are excellently fit by power laws.
Figures~\ref{fig:rheologysummary}(a)--(c) show the data for Type I, Type
II and Type III JPs, respectively, under both shear flow (squares) and
TG flow (triangles). The bilayer phases consisting of Type I JPs are
basically Newtonian with viscosity $0.014$ MPa\;$\upmu$s $= 14$ mPa\;s,
about 14 times the viscosity of water at room temperature
(Figures~\ref{fig:rheologysummary}(a), dashed curve). The vesicle
bilayer phase is slightly shear thickening
(Figure~\ref{fig:rheologysummary}(a), solid curve). Similar shear
thickening behaviors are found in continuum vesicle
models~\cite{rah-vee-bir2010,NaitOuhra2019RheologyOA}.
The multilamellar phase consisting of
Type II JPs is somewhat shear thinning, but its viscosity is larger than
for Type I. Finally, the striated phase is strongly shear-thinning. This
further explains the rigid-like behavior of the striated phase found in
the strain, shear-rate relationships from
Figures~\ref{fig:s2esummary}(a) and (b) (triangles).

@@

The calculated viscosities---14~mPa~s for Type I and 21~mPa~s for Type
II JP phases---are physically reasonable. In two-dimensional dilute
suspensions, the Einstein viscosity correction is $1 + 2 \phi + 4\phi^2
+ O(\phi^3)$, where $\phi \ll 1$ is the volume
fraction~\cite{PhysRevFluids.1.043301, Haines2011APO, Khair2006TheC,
Brady1983TheEV}. In Figures~\ref{fig:s2esummary}(e)--(h), the volume
fraction is $\phi \approx 0.5$, which would correspond to a effective
shear viscosity of $4$~mPa~s according to Einstein's viscosity
correction. Note, however, that since $\phi = 0.5$ is outside of the
dilute limit, one expects viscosities ten or more times greater than the
viscosity of water~\cite{Konijn2014ExperimentalSO}
and number of analytical and numerical
approaches have been successfully applied to these dense suspensions
\citep{Guazzelli2018RheologyOD}.

Further parametric studies are required to differentiate
between passive effects and JPs' preferred alignments. 
For example, the difference between the values 14~mPa~s for Type I and
21~mPa~s for Type II JPs can be explained by the fact that the
multilamellar phase is more tightly packed than the bilayer phase
(Figures \ref{fig:s2esummary}(e)--(h)). Furthermore, it seems that the
viscosity, and the tendency toward shear thinning in the case of Type
III JPs where viscosity is effectively infinite for low strain rates
(Figure~\ref{fig:rheologysummary}(c)), is related to particle
coordination. That is, a single JP coordinates with: one
neighbor in the apposing bilayer for Type I, two neighbors at the tail
and head interfaces for Type II, and four neighbors (front, back, left,
and right) for Type III.

Scaling laws for the ``virial viscosity'', the nonhydrodynamic part of the
relative viscosity in steady shear, have 
been determined experimentally~\citep{PhysRevFluids.5.053302}. 
Other simulation studies have investigated the rheology of strain-hardening
capsules as a function of membrane inexstensibility
using the three-dimensional immersed boundary method~\cite{aouane_scagliarini_harting_2021},
dilute suspensions of compound particles~\cite{singeetham_chaithanya_thampi_2021},
and shown how shear
thickening in systems with widely different particle properties stems 
arise when adhesion forces bring particles into frictional contact
~\cite{PhysRevFluids.7.054302}. Within this context, membrane inexinsibility
in the case of Type I amphiphiles and adhesion in general 
can be inferred from the functional relationships between free energy
and displacement in Figure~\ref{fig:fsummary}(c), for example.

For active particles, researchers have 
obtained analytical expressions for the effective viscosity
resulting from the activity of dilute swimmers
in extensional flows
~\cite{Saintillan2010ExtensionalRO} and compared
numerical predictions under shear flow derived from
Stokesian dynamics and lubrication theory~\cite{ishikawa_brumley_pedley_2021}.
Suspensions of pushers can yield an apparent reduction
in viscous dissipation arising from particle activity
In contrast, the JP suspensions of the present study
do not inject, but rather store energy coming from the
background flow.
